# Loading twitter json files in R

R is adept at working with real data. As a conseqence, many packages
have been developed for extracting data from various formats and dumping
them into standard R *classes* such as data.frame, list or even
SpatialPolygonsDataFrame.

.json is an increasingly common file format. Here we see how to access
the data within .json files, using the library **rjson**. If you do not have
this package already, `install.packages(rjson)` will install it.
Let's try opening up some twitter data.

```{r}
library(rjson)
tweet <- fromJSON(file = "data/tweets.json") # loads 1st tweet, but no more
names(tweet) # show the list names - what data has been loaded
tweet$text # the text
```

To load more than one tweet in R using this library, the code gets more complex:

```{r}
ts <- fromJSON(sprintf("[%s]", paste(readLines("data/tweets.json"),collapse=",")))
ts[[2]]$text
ts[[1]]$coordinates$coordinates # the coordinates
```

The above code shows that each tweet's information is now stored as
a separate list item. `ts` is a series of lists within lists!
Extracting the data into a neat data frame requires the use of the bizarre
`sapply` function:

```{r}
sapply(ts, function(x) x$coordinates$coordinates )[[1]] # the extracted coords
coords <- matrix(unlist(sapply(ts, function(x) x$coordinates$coordinates )), ncol=2, byrow=T)
coords <- as.data.frame(coords)
coords # successful extraction of coordinates
```

The method is the same for any attribute.
Let's extract the text variable, as an example, and add it to the
coordinates data:

```{r}
text <- sapply(ts, function(x) x$text )
text <- unlist(text)[-1]
text[1:3]
text <- iconv(text, from="ASCII", "UTF-8")
text <- strtrim(text, 5)

tdf <- data.frame(text = text) # create R data.frame
tdf <- cbind(tdf, coords)
tdf
```

Let's plot the data (in a very rudimentary form) to prove we have 'geotagged'
data:

```{r}
plot(tdf$V1, tdf$V2, col="red")
text(tdf$V1, tdf$V2, labels=tdf$text)
```

```{r}
findOffendingCharacter <- function(x, maxStringLength=256){  
  print(x)
  for (c in 1:maxStringLength){
    offendingChar <- substr(x,c,c)
    print(offendingChar) #uncomment if you want the indiv characters printed
    #the next character is the offending multibyte Character
  }    
}

findOffendingCharacter(text)

```

## Loading 'Big' Twitter datasets

If you have many Tweets (upwards of a few Gb), you need to
take this into account when loading them

### Splitting large files with `split`

### Adding robustness to your loop

Sometimes `for` loops will fail due to a single error, e.g.:

```{}
[1] "28.4262048192771% done"
Error in fromJSON(sprintf("[%s]", paste(readLines(i), collapse = ","))) : 
  incomplete list - missing :
In addition: Warning message:
In readLines(i) :
  incomplete final line found on 'data/chunked//t1403301271285.jsondh'
```

It is far preferable to continue

