---
title: "Pennine way tweets"
output: html_document
---

# Loading the data

The data was loaded from an sql database originally created by Kirk Harland:

```{r}
# geoT <- SpatialPointsDataFrame(coords= matrix(c(db$Lon, db$Lat), ncol=2), data=db)
load("../tweet_store/.RData")
```

# Analysis of the full dataset

The full twitter dataset contains 2.8 million tweets collected between September 2011 and April 2012.
The bounding box of the tweets encapsulates Leeds and Bradford, with the highest density of tweets
focussed on Leeds city centre. A range of variables were collected, but the subsequent
analysis will focus on `Text`, the written content of each tweet. This is shown below:


```{r}
names(geoT) # the variables available for analysis
nrow(geoT) / 1000000 # million tweets
range(geoT$Time)
summary(nchar(geoT$Text))
geoT[ which.max(nchar(geoT$Text)), ]

# plotting the spatial distribution of the tweets
library(ggmap)
ggmap(get_map(bbox(geoT))) + geom_point(data = geoT@data[sample(1:nrow(geoT), size = nrow(geoT) / 10), ],
                                        aes(x = Lon, y = Lat), alpha = 0.1)
```

# Subsetting 'Pennine Way'

Below we see tweets related to the Pennine Way

```{r}
length(grep("pennine way", geoT$Text, ignore.case = T))
head(geoT$Text[grep("pennine way", geoT$Text, ignore.case = T)])

length(grep("pennine", geoT$Text, ignore.case = T))
head(geoT$Text[grep("pennine", geoT$Text, ignore.case = T)])
pTweets <- geoT[ grep("pennine", geoT$Text, ignore.case = T) , ]
```

# Buffer around Pennine way

The coodinates of the Pennine Way can be downloaded directly from
the internet, from [hiking.waymarkedtrails.org/en/](http://hiking.waymarkedtrails.org/en/):

```{r}
download.file(url = "http://hiking.waymarkedtrails.org/en/routebrowser/63872/gpx", "pennine.gpx")
library(rgdal)
ogrListLayers("pennine.gpx")
pw <- readOGR("pennine.gpx", layer = "tracks")
pw <- spTransform(pw, CRS("+init=epsg:27700")) # transform CRS to OSGB
library(rgeos)
pwBuf <- gBuffer(pw, width = 5000) # create buffer
plot(pwBuf) # plot to test dimensions make sense
pwBuf <- spTransform(pwBuf, CRS("+init=epsg:4326"))
proj4string(geoT) <- CRS("+init=epsg:4326")
PennineTweets <- geoT[pwBuf, ]
nrow(PennineTweets)
plot(pwBuf)
points(PennineTweets)
```

Unfortunately, the buffer for the Pennine Way only just intersects with the edge of the
twitter dataset - resulting in just over 50,000 tweets. All of these are over 10 km away,
so they cannot be classed as Pennine Tweets.

# Downloading the 'Pennine Tweets'

The Twitter dataset we've looked at is unlikely to be of much use as it
does not actually intersect with the Pennine Way. However, the method for
extracting 'Pennine Tweets' has been demonstrated and some example tweets
have been filtered from the original dataset of 2.8 million tweets.

These were saved to my Dropbox file with the following command:

```{r}
write.csv(pTweets, "~/Dropbox/Public/tmp/ptweets.csv")
```

The data can be downloaded from [here](https://dl.dropboxusercontent.com/u/15008199/tmp/ptweets.csv).

# Further work

There is an ongoing project to download all geographic tweets nationwide,
which can be found on the [tweepy](https://github.com/Robinlovelace/tweepy) repository.
This may provide better Twitter data on the Pennine trail but hopes should not be high:
ramblers, except for [RamblersGB](https://twitter.com/RamblersGB) are not known for their tweeting ways!
